Titeln på avhandlingens språk

### 2022-09-07 background.tex
tweaks, zero-wait to greedy

Current implementations, such as those in~\cite{Chen2015LEGO,Chen2018application}, employ \emph{zero-wait} sampling.
In this scheme, a new sample is immediately taken as soon as an acknowledgement is received for the previous sample.
This means that the interval between these sampling instants is not necessarily constant, as it is subject to fluctuations due to resource contention on both the network and compute side.
It also has as a consequence that acknowledgements must be provided even for those samples which do not cause the generation of a new instruction --- these acknowledgements are simply used for flow control and do not generate user-noticeable feedback.

Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling intervals (following a zero-wait scheme) at which the \ac{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e. which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
If we define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), it must follow that (see also~\cite{olguinmunoz:impact2021})\footnote{\( U(a, b) \) represents the continuous uniform distribution in the open interval \( (a, b) \).}
\begin{align}\label{eq:tc}
    t_c &\thicksim U(t_{n - 1}, t_n)
\end{align}

>>>>

Current implementations, such as those in~\cite{Chen2015LEGO,Chen2018application}, employ \emph{greedy} sampling.
In this scheme, a new sample is immediately taken as soon as an acknowledgement is received for the previous sample.
This means that the interval between these sampling instants is not necessarily constant, as it is subject to fluctuations due to resource contention on both the network and compute side.
It also has as a consequence that acknowledgements must be provided even for those samples which do not cause the generation of a new instruction --- these acknowledgements are simply used for flow control and do not generate user-noticeable feedback.

Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling intervals (following a greedy scheme) at which the \ac{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e. which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
If we define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), it must follow that (see also~\cite{olguinmunoz:impact2021})\footnote{\( U(a, b) \) represents the continuous uniform distribution in the open interval \( (a, b) \).}
\begin{align}\label{eq:tc}
    t_c &\thicksim U(t_{n - 1}, t_n)
\end{align}

### 2022-09-07 model.tex
tweaks, zero-wait to greedy

\begin{figure*}
    \centering
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/imp_neur_vs_exectime.png}
        \caption{}\label{fig:timing:impneurvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{%
        Visualizations of the model data after discretization and post-processing.
        \subref{fig:timing:impneurvsetime} illustrates the effect of impairment on execution times, and how neuroticism modulates this behavior;
        \subref{fig:timing:durvsetime} exemplifies how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021};
        finally, \subref{fig:timing:imptransvsetime} shows the lingering effects of impairment after a transition.
    }\label{fig:timing}
\end{figure*}

@@

\subsection{Model verification}
\todo[inline]{Needs better name.}

@@

These models are integrated into client software for communicating with an adapted and instrumented version of the Gabriel~\cite{Chen2015LEGO,Chen2018application} \ac{WCA} backend running variants of the LEGO task.
In the following, we use these client-server loops to illustrate the implications of the realistic timing models, which react to changes in system responsiveness in real-time, when compared to the static, naive model.
Two scenarios are studied, using the testbed shown in \cref{fig:expsetup}:
\begin{enumerate}
    \item\label{verification:scaling} A scenario to study the effects of decreasing system responsiveness due to resource and network congestion.
    An increasing number of client-server loops (\numlist{1;4;7;10} loops) are deployed in parallel for each model.
    Neuroticism is set to a constant value of \num{0.5}, and each combination of model and number of clients is repeated \num{5} times for better statistical representativeness.
    \item\label{verification:neuro} A scenario in which the effects of neuroticism are studied.
    Two different configurations of the realistic models, with neuroticism values of \num{0.0} (\emph{low}) and \num{1.0} (\emph{high}), are compared to a reference setup using the naive model.
    In all these setups, \num{9} loops are deployed in parallel, and an \emph{iperf3}\footnote{\href{https://iperf.fr/}{https://iperf.fr/}} client-server pair is deployed between the tenth Raspberry Pi client and the cloudlet.
    The \emph{iperf3} deployment is configured to generate additional network load by constantly sending \SI{1460}{\byte} \ac{UDP} datagrams on the uplink; the rate at which these datagrams are sent is being limited by the \acs{CPU} of the Raspberry Pi client.

@@

Both scenarios described above use a variant of one of the \num{169}-step tasks used in~\cite{olguinmunoz:impact2021}, truncated to \num{45} steps.

\begin{figure}
    \centering
    \includegraphics[width=.8\columnwidth]{figs/numclients_vs_duration.png}
    \caption{
        Consequences of decreased system responsiveness due to resource and network congestion.
        We can evidence both how the realistic models speed up at with respect to the naive model when completely unimpaired, and how these same models strongly slow down as system impairment increases.
    }\label{fig:scaling_duration}
\end{figure}

\cref{fig:scaling_duration} shows the results for scenario \labelcref{verification:scaling}.

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/imp_neur_vs_exectime.png}
        \caption{}\label{fig:timing:impneurvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{%
        Visualizations of the model data after discretization and post-processing.
        \subref{fig:timing:impneurvsetime} illustrates the effect of impairment on execution times, and how neuroticism modulates this behavior;
        \subref{fig:timing:durvsetime} exemplifies how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021};
        finally, \subref{fig:timing:imptransvsetime} shows the lingering effects of impairment after a transition.
        Error bars indicate the \SI{95}{\percent} \ac{CI}.
    }\label{fig:timing}
\end{figure*}

@@

\subsection{Model verification}\label{ssec:model:verification}
\todo[inline]{Needs better name.}

@@

These models are integrated into client software for communicating with an adapted and instrumented version of the Gabriel~\cite{Chen2015LEGO,Chen2018application} \ac{WCA} backend running variants of the LEGO task.
In the following, we use these client-server loops to illustrate the implications of the realistic timing models, which react to changes in system responsiveness in real-time, when compared to the static, naive model.
Two scenarios are studied, using the testbed shown in \cref{fig:expsetup}:
\begin{enumerate}
    \item\label{verification:scaling} A scenario to study the effects of decreasing system responsiveness due to resource and network congestion.
    An increasing number of client-server loops (\numlist{1;4;7;10} loops) are deployed in parallel for each model.
    Neuroticism is set to a constant value of \num{0.5}, and each combination of model and number of clients is repeated \num{5} times for better statistical representativeness.
    \item\label{verification:neuro} A scenario in which the effects of neuroticism are studied.
    Two different configurations of the realistic models, with neuroticism values of \num{0.0} (\emph{low}) and \num{1.0} (\emph{high}), are compared to a reference setup using the naive model.
    In all these setups, \num{9} loops are deployed in parallel, and an \emph{iperf3}\footnote{\href{https://iperf.fr/}{https://iperf.fr/}} client-server pair is deployed between the tenth Raspberry Pi client and the cloudlet.
    This \emph{iperf3} deployment starts \SI{120}{\second} after the start of the \num{9} model loops, and is configured to generate additional network load by constantly sending a stream of \SI{1460}{\byte} \ac{UDP} datagrams on the uplink; the rate at which these datagrams are sent is only limited by the \acs{CPU} of the Raspberry Pi client.

@@

Both scenarios described above use a variant of one of the \num{169}-step tasks used in~\cite{olguinmunoz:impact2021}, truncated to \num{45} steps.
\medskip

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\textwidth]{figs/numclients_vs_duration.png}
        \caption{
            Consequences of decreased system responsiveness due to resource and network congestion.
            We can evidence both how the realistic models speed up with respect to the naive model when completely unimpaired, and how these same models strongly slow down as system impairment increases.
        }\label{fig:scaling_duration}
    \end{subfigure}%
    \hspace{\fill}%
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\textwidth]{figs/neuroticism_vs_duration.png}
        \caption{}\label{fig:neuro_duration}
    \end{subfigure}%
    \caption{Results for both scenarios described in \cref{ssec:model:verification}. Error bars indicate the \SI{95}{\percent} \ac{CI}.}
\end{figure*}

\cref{fig:scaling_duration} illustrates the results for scenario \labelcref{verification:scaling}. 
It showcases the important behaviors of the realistic models which are not captured by naive, non-adaptive model.
On one hand, the realistic models (and by extension, humans) are actually faster than the naive model by up to \SI{4.37}{\percent} at the lowest level of impairment.
This is due to the speed-up effect described in \textcite{olguinmunoz:impact2021} --- humans get faster as a task progresses with a high system responsiveness.

On the other, the realistic models experience a slowdown of about \SI{5.13}{\percent} at the highest levels of impairment when compared to the naive model.
This is explained by the reduced system responsiveness either negating the speed-up effect, or directly leading to the \emph{additional} behavioral slowdown previously described~\cite{olguinmunoz:impact2021}.
It should be noted that for the \numlist{7;10} client setups only about \SI{6}{\percent} and \SI{22}{\percent} of \acp{TTF} fell into the medium impairment level, and practically no \acp{TTF}
